### 2017-06-15 architecture.tex
Added export and access flows

\begin{itemize}
\item request access
\item grant access
\item submit job
\item fetch data
\item compute
\item store results
\end{itemize}

@@

\begin{itemize}
\item Export request
\item Initiate export
\item Export data
\item Access results
\end{itemize}

>>>>

Bob an analyst authenticates on the system and requests access to a private safe-collection.
The request is now visible on the stewarship dashboard of all stewards. Alice, a steward for the requested
safe-collection approves the request for n days. The approval process adds the appropriate policies to the
safe-collection granting access to Bob. Bob now can submit tasks via the  REST api, that specify data-items
from the safe-collection as inputs. The REST api marks the task as export controlled since it draws results
from an export controlled safe-collection. The submitted task is posted to an internal queue from which a
worker node in the \NAME private subnet picks up Bob's task. The worker node assumes Bob's identity and with
his credentials requests data from the safe-collection. Since Bob now has read privileges for the
safe-collection, the data is fetched to the worker node, on which the analysis task is executed.
Upon completion, the worker node puts the generated results under the outputs directory of the safe-collection
since the task used export controlled data. Bob's analysis is now complete, but he is unable to view the
results.

@@

Once Bob's analysis task is complete Bob realizes that he requires export approval before he may view the
results, so he issues a request for export. Alice, sees a new export request on her dashboard. Alice assumes
the steward role with a fresh authenticated token, and accesses the results and the complete description
of Bob's analysis task. Once Alice deems the results safe for export, she initiates data export. \NAME
services use Alice's temporary credentials to transfer the results from the safe-collection to a public
safe-collection and updates the task information with new location of the results. Bob can now log on
and view or download the results.
